temp - Results

### 2025-04-11 Manuscript_ScoreReLiability.qmd
text updates

---
title: "Score ReLiability? Exploring the role of score reliability for effect size heterogeneity"
format: html
editor: visual
---

@@

@@

*Table 3*

>>>>

---
title: "Score ReLiability? Exploring the role of score reliability for effect size heterogeneity"
sbutitle: ""
format: html
editor: visual
author: "Beinhauer, L.J., Fünderich, J.H., Renkewitz, F."
engine: knitr
---

@@

Re-arranging equation [-@eg-HS] leads to the following equation:

$$Var(\delta) = \frac{Var(\delta_0) - [E(\delta)]^2 Var(a)}{E[a^2]}$$ {#eq-HS_r}

where:
$$E(\delta) = \frac{E(\delta_0)}{E(a)}$$ {#eq-HS_E}

$$

@@

{{< pagebreak >}} 
*Table 3*

### 2025-04-11 temp_results.qmd

To assess whether actual differences in score reliability existed, heterogeneity in score reliability is assessed across all four projects, making use of Reliability Generalization Meta-Analysis.

>>>>

To assess whether actual differences in score reliability existed, heterogeneity in score reliability is assessed across all four projects, making use of Reliability Generalization Meta-Analysis.
Table 1 briefly summarises the results concerning differences in score reliability.
From Cochran's Q-test, a hypothesis test on whether heterogeneity is larger than zero, we can gather that for the scales measuring all four phenomena, score reliability differs across samples.
The individual heterogeneity in score reliabiliy tau_alpha, is rather low for the phenomena of Nosek, PSACR001 Anxiety, and PSACR002 negative photo.
This is likely due to the higher levels of score reliability, averaging at least `r round(min(B_alpha_rma_df$mu_alpha[B_alpha_rma_df$mu_alpha >= .7]), 2)`.
However, even for the phenomenon PSACR001_behav_int, where true mean score reliability is below .7 and the heterogeneity is rather large with tau_alpha = `r round(B_alpha_rma_df$tau_alpha[B_alpha_rma_df$mu_alpha < .7], 2)`, correcting for differences score reliability does not reduce ES heterogeneity.
The analysis of score reliability highlights that the lack of reduction in corrected ES heterogeneity can not be explained away by a lack of variation in reliability or "insufficiently imperfect" reliability.

```{r, echo = FALSE}
tab_df <- B_alpha_rma_df %>% 
  select(MASC, mu_alpha, tau_alpha, QE, k, QEp) %>% 
  mutate(QEp = ifelse(QEp < .001, "<.001", QEp))

knitr::kable(tab_df, digits = 3)
```
